\documentclass{recipe}

\begin{document}
\begin{recipe}{Spagetti Carbonara}
  \servings{2}

  \begin{ingredients}
    \ingredient{1}{tbsp}{butter}
    \ingredient{3}{tbsp}{olive oil}
    \ingredient{1}{oz}{bacon}
    \ingredient{1}{large}{egg}
    \ingredient{\half}{oz}{Parmasean Cheese}
    \ingredient{10}{oz}{spagetti}
  \end{ingredients}

  \begin{steps}
  \item Start pasta water boiling
  \item Beat the egg and mix in the parmasean cheese.
  \item When the water comes to a boil, add in the pasta.
  \item Finely chop the bacon and add it to a pot along with the olive
    oil.
  \item Half way through cooking the pasta, add a few tablespoons of
    the pasta water to the bacon te stop the cooking process.  You'll
    end up boiling off most of this water so the amount really depends
    on how hot your stove is.
  \item When the pasta is done cooking, drain it and add it along with
    the butter to the pot with the bacon and oil in it.  Mix this well
    to season the pasta.
  \item Remove the bacon pot from the heat.
  \item Drizzle the egg mixture into the pasta while stirring
    vigorously to avoid scrambling the eggs.
  \item Stir until the egg mixture is cooked (maybe 15 seconds) and
    then remove from the pot to avoid burning.
  \end{steps}

  \begin{notes}
  \item A second egg and extra cheese substituted for the butter will
    make a thicker sauce, but it's a bit too thick for two people.
    It's probably best to have 2 eggs per 3 people, with no extra
    butter.
  \end{notes}
\end{recipe}
\end{document}
